---
title: "Data sets from Google, Indeed and Kaggle"
author: "[Kleber Perez - `r format(Sys.Date(), '%B %d, %Y')`](https://www.linkedin.com/in/kleberperez/)" 
output: 
  html_document:
    code_folding: show
    theme: flatly
    highlight: pygments
    css: ./p2css.css
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
#install.packages("RMySQL")
# 1. Library
library(RMySQL)
library(tidyverse)
library(kableExtra)
library(plotly)
library(ggplot2)
```

<div class="jumbotron jumbotron-fluid">

## Load [data source](https://github.com/LovinSpoonful/) into an R dataframe using MySQL RDBMS

> Each data has a time constraint and had time box, but the efforts to have raw data to provide downstream on this project. The following data resource from Google, Indeed and Kaggle Job Boards generalize the approach to initiate a search for "data science" terms to collect the results, identify the skills and a preliminary filtering of noise and irrelevant data. The results set is provided to transforming the data with the following variables: Skill Type, Skill name, rating and company name. 

</div>

```{r}
# 2. variables Settings
db_user <- 'root'
db_password <- ''
db_name <- 'skills'
db_host <- '127.0.0.1' # localhost for local access
db_port <- 3306

# 3. Read data from db
mydb <-  dbConnect(MySQL(), user = db_user, password = db_password,
                 dbname = db_name, host = db_host, port = db_port)
s <- paste0(" SELECT SkillType, SkillName, Rating,
                  		CASE
                  			WHEN Company = 1 THEN 'Google'
                  			ELSE 'NA'
                  		END AS Company
              FROM GoogleData
              UNION
              SELECT SkillType, SkillName, Rating,
                  		CASE
                  			WHEN Company = 2 THEN 'Indeed'
                  			ELSE 'NA'
                  		END AS Company
              FROM IndeedData
              UNION
              SELECT SkillType, SkillName, Rating,
                  		CASE
                  			WHEN Company = 3 THEN 'Kaggle'
                  			ELSE 'NA'
                  		END AS Company
              FROM KaggleData;")

rs <- dbSendQuery(mydb, s)
df <-  fetch(rs, n = -1)
on.exit(dbDisconnect(mydb))

#uf <- df %>% gather(SkillName, n, Rating:Company)
kable(df) %>%
  kable_styling() %>%
  scroll_box(height = "500px")


```

## Summary

```{r df}
summary(df)
```

## Including Plots

<div class="jumbotron jumbotron-fluid">

```{r, echo=FALSE}
f <- as.factor(df$SkillType)
levels(f)
plot(f, df$Rating)

#get all resource information per company

ggplot(df, aes(x=SkillType, y=Rating, fill=Company)) +
 geom_bar(stat="identity") +
 guides(fill=guide_legend(reverse=TRUE)) +
 expand_limits(x= 0, y = 0)

# Summarize the median gdpPercap by year & continent, save as by_year_continent
by_Skill_Rating <- df %>%
  group_by(SkillType) %>%
  summarize(medianRating = median(Rating))

ggplot(by_Skill_Rating, aes(x=SkillType, y=medianRating)) +
  geom_point() +
  expand_limits(x= 0, y = 0)

```

</div>

<br />

<div class="jumbotron jumbotron-fluid">

## Conclusion

> The purpose of this exercise is to import three data sets in mysql db and tidy them with above libraries. 




(1) Project 3 on rpubs.com, and SQL script and additional files uploaded on github.

<div class=""> 
<div class="alert alert-info" role="alert"> 
 <p>
  <a href="http://rpubs.com/kleberperez/476878" class="btn btn-default" role="button">&nbsp; rpubs &nbsp; </a> 
  &nbsp; &nbsp; &nbsp;
  <a href="https://github.com/kleberperez1/CUNY-SPS-Data607-Tidy-Data" class="btn btn-default" role="button"> &nbsp; github &nbsp; </a>
 </p>
</div> 
</div> 

</div>

<br />

* * *

<br />
<br />

> *Please email to: * <a href="mailto:kleber.perez@live.com">kleber.perez@live.com</a> *for any suggestion.*

<footer class="border-top text-muted fixed-bottom">

        DATA607 Project 2 - MSDS 2019 Program.

</footer>

\textbf{Text ignored: END of other links}

<br />
<br />


